Backscatter Modulation Design for Symbiotic Radio Networks

### 2022-01-26 main.tex
:pencil: Update thresholding proof

			\begin{theorem}
				If any $L$-input ($L \in \mathbb{Z}_{++}$) continuous-output channel follows Erlang distribution~\eqref{eq:energy_distribution}, then the optimal number of thresholds is $L+1$ and the capacity-achieving decision region $j$ has convex structure $\mathcal{R}_j^{\star} = [t_{j-1}^{\star}, t_j^{\star})$.
			\end{theorem}

			\begin{proof}
				For any finite number of thresholds $S \in \mathbb{Z}_{++}$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in definition, since otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$. Without loss of generality, we assume
				% $L \mid S$ and
				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{Note that the proof holds for general mapping and we focus on this case for the ease of notation.} The thresholding design problem can be expressed as
				\begin{maxi!}
					{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(c_{\mathcal{K}};z)}{\label{op:thresholding}}{\label{ob:backscatter_mutual_information}}
					\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
				\end{maxi!}

				Problem~\eqref{op:thresholding} is intricate due to the strict inequality constraint~\eqref{co:strict_inequality}. Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate the original constraints. The Lagrangian function for the relaxed problem is
				\begin{equation}
					L(\boldsymbol{t},\boldsymbol{\mu}) = - I_{\mathrm{B}}(c_{\mathcal{K}};z) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
					% = \sum_{j \in \mathcal{L}} P(\bar{z}_j) \log P(\bar{z}_j) - \sum_{i \in \mathcal{L}} \sum_{j \in \mathcal{L}}
				\end{equation}
				where $\mu_s$ is the Lagrange multiplier associated with the non-strict counterpart of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$. The corresponding \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
				\begin{subequations}
					\begin{equation}
						- \nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) + \mu_{s-1}^{\star} - \mu_s^{\star} = 0,
						\label{eq:stationarity}
					\end{equation}
					\begin{equation}
						\mu_s^{\star} \ge 0,
						\label{eq:dual_feasibility}
					\end{equation}
					\begin{equation}
						\mu_s^{\star} (t_{s-1}^{\star} - t_s^{\star}) = 0.
						\label{eq:complementary_slackness}
					\end{equation}
				\end{subequations}
				Since we require $t_{s-1} < t_s$ by definition, \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} imply $\mu_s^{\star} = 0$, $\forall s \in \mathcal{S}$. Therefore, \eqref{eq:stationarity} reduces to
				\begin{equation}
					\nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) = 0.
				\end{equation}
			\end{proof}

@@

				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,

@@

						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states}\\
						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{eq:dropped_states}

@@

						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) + \nu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,

@@

						\lambda_{k,m_k}^{\star} = 0, \quad P_k^{\star}(\bar{c}_{m_k}) > 0,

@@

						\lambda_{k,m_k}^{\star} \ge 0, \quad P_k^{\star}(\bar{c}_{m_k}) = 0,

@@

					\nabla_{P_k^{\star}(\bar{c}_{m_k})} I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).

@@

				Due to the necessity and sufficiency of the \gls{kkt} conditions, we conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
				\begin{subequations}
					\begin{alignat}{2}
						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & = \nu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
						I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) & \le \nu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
					\end{alignat}
				\end{subequations}
				which implies
				\begin{equation}
					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \nu_k^{\star} + (1 - \rho).
				\end{equation}

				On the other hand, by definition of marginations \eqref{eq:backscatter_sum_rate_expectation}, \eqref{eq:primary_ergodic_rate_expectation} and weighted summations \eqref{eq:weighted_sum_marginal_information}, \eqref{eq:weighted_sum_rate}, we have
				\begin{equation}
					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z),
				\end{equation}
				which is irrelevant to $k$. It suggests $I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \nu_k^{\star} + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
			\end{proof}

@@

				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_k(\bar{c}_{m_k})$ and is maximized at $\nabla_{P_k^{\star}(\bar{c}_{m_k})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, namely

@@

					S_k'(\bar{c}_{m_k}) - S_k'(\bar{c}_{i_k}) + (1 - \rho) \log \frac{P_k(\bar{c}_{i_k})}{P_k^{\star}(\bar{c}_{m_k})} = 0,

@@

				% 		P_k^{\star}(\bar{c}_{m_k})

@@

						P_k^{\star}(\bar{c}_{m_k})

@@

				where we define $u_k'(\bar{c}_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(\bar{c}_{m_k};\boldsymbol{y},z) \right)$. Although $P_k(\bar{c}_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^{\star}(\bar{c}_{m_k})$ is not guaranteed to be optimal, it has exactly the same form as \eqref{eq:optimal_relative_distribution}. In such case, the solution of choosing $i_k$ as reference would coincide with that of choosing any $m_k \ne i_k$ as reference, while optimality for $i_k$ is guaranteed in the latter case. Therefore, for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $\forall i_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$, \eqref{eq:optimal_relative_distribution} ensures

@@

				We then prove any converging point of sequence \eqref{eq:optimal_distribution}, denoted as $P_k^{\star}(\bar{c}_{m_k})$, fulfills the optimal conditions \eqref{eq:optimal_conditions} and achieves the weighted primary-backscatter sum capacity. To see this, define
				\begin{equation}
					D_k^{(r)}(\bar{c}_{m_k}) \triangleq \frac{P_k^{(r+1)}(\bar{c}_{m_k})}{P_k^{(r)}(\bar{c}_{m_k})} = \frac{u_k^{(r)}(\bar{c}_{m_k})}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k^{(r)}(\bar{c}_{m_k'})},
				\end{equation}
				where $P_k^{(0)}(\bar{c}_{m_k}) > 0$. As sequence \eqref{eq:optimal_distribution} is convergent, any state with $P_k^{\star}(\bar{c}_{m_k}) > 0$ need to satisfy $D_k^{\star}(\bar{c}_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(\bar{c}_{m_k}) = 1$, namely
				\begin{equation}
					I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k^{\star}(\bar{c}_{m_k'}),
				\end{equation}
				which coincides with \eqref{eq:probable_states_marginal} and implies \eqref{eq:probable_states}. That is, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
				On the other hand, we assume $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
				% On the other hand, we show if $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:optimal_distribution}. By this assumption, for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
				\begin{equation}
					I_k^{\star}(\bar{c}_{m_k};\boldsymbol{y},z) > I^{\star}(c_{\mathcal{K}};\boldsymbol{y},z) = \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) I_k^{\star}(\bar{c}_{m_k'};\boldsymbol{y},z),
				\end{equation}
				where the equality origins from \eqref{eq:backscatter_sum_rate_expectation} and \eqref{eq:primary_ergodic_rate_expectation}. Since the exponential function is monotonically increasing, we have $u_k^{\star}(\bar{c}_{m_k}) > \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k^{\star}(\bar{c}_{m_k'})$ and $D_k^{\star}(\bar{c}_{m_k}) > 1$. Considering $P_k^{(0)}(\bar{c}_{m_k}) > 0$ and $P_k^{\star}(\bar{c}_{m_k}) = 0$, it contradicts with
				\begin{equation}
					P_k^{(r)}(\bar{c}_{m_k}) = P_k^{(0)}(\bar{c}_{m_k}) \prod_{n=1}^r D_k^{(n)}(\bar{c}_{m_k}).
				\end{equation}
				Therefore, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.

>>>>

			\begin{theorem}
				If any $L$-input continuous-output channel follows Erlang distribution~\eqref{eq:energy_distribution}, then the optimal number of thresholds is $L+1$ and the capacity-achieving decision region $j$ has convex structure $\mathcal{R}_j^\star = [t_{j-1}^\star, t_j^\star)$.
			\end{theorem}

			\begin{proof}
				For any finite number of thresholds $S \ge L+1$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in the definition, as otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$. Without loss of generality, we assume
				% $L \mid S$ and
				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{The proof holds for general mapping $R_s \mapsto \mathcal{R}_j$, and we focus on this specific case for the ease of notation.} The thresholding design problem can be expressed as
				\begin{maxi!}
					{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(c_{\mathcal{K}};z)}{\label{op:thresholding}}{\label{ob:backscatter_mutual_information}}
					\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
				\end{maxi!}

				Problem~\eqref{op:thresholding} is intricate due to the strict inequality constraint~\eqref{co:strict_inequality}. Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate the original constraints. The Lagrangian function for the relaxed problem is
				\begin{equation}
					L(\boldsymbol{t},\boldsymbol{\mu}) = - I_{\mathrm{B}}(c_{\mathcal{K}};z) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
					% = \sum_{j \in \mathcal{L}} P(\bar{z}_j) \log P(\bar{z}_j) - \sum_{i \in \mathcal{L}} \sum_{j \in \mathcal{L}}
				\end{equation}
				where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$. The corresponding \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
				\begin{subequations}
					\label{eq:kkt_thresholding}
					\begin{equation}
						- \nabla_{t_s^\star} I^\star_{\mathrm{B}}(c_{\mathcal{K}};z) + \mu_{s-1}^\star - \mu_s^\star = 0,
						\label{eq:stationarity}
					\end{equation}
					\begin{equation}
						\mu_s^\star \ge 0,
						\label{eq:dual_feasibility}
					\end{equation}
					\begin{equation}
						\mu_s^\star (t_{s-1}^\star - t_s^\star) = 0.
						\label{eq:complementary_slackness}
					\end{equation}

				\end{subequations}
				Due to the strict inequality constraint~\eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$. For \gls{dmtc} based on energy detection~\eqref{eq:energy_distribution}, it is trivial to conclude $t_0^\star = 0$ and $t_S^\star = \infty$. Hence, we focus on $s' \in \mathcal{S} \setminus \{S\}$ and \eqref{eq:kkt_thresholding} reduces to
				\begin{equation}
					\nabla_{t_{s'}^\star} I^\star_{\mathrm{B}}(c_{\mathcal{K}};z) = 0,
				\end{equation}
				that is, for $j \in \mathcal{L}$ and $j \equiv s' \pmod L$,
				\begin{equation}
					\sum_l a_{l,j} f(t_{s'}^\star \mid x_l) = 0,
					\label{eq:kkt_thresholding_explicit}
				\end{equation}
				where
				\begin{equation}
					a_{l,j} =
					\begin{cases}
						P(x_l) \log \frac{P(x_l \mid z_{j+1}^\star)}{P(x_l \mid z_j^\star)}, & j \in \mathcal{L} \setminus \{L\},\\
						P(x_l) \log \frac{P(x_l \mid z_{1}^\star)}{P(x_l \mid z_j^\star)}, & j = L.
					\end{cases}
				\end{equation}

				Since the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane~\cite{Nguyen2020a}, the sequence $(a_{l,j})_{l=1}^{L}$ only change sign once for a given $j$. Besides, we notice the LHS of~\eqref{eq:kkt_thresholding_explicit} is a generalized Dirichlet polynomial, as $f(t_{s'}^\star \mid x_l)$ follows Erlang distribution~\eqref{eq:energy_distribution}. By Descartes' rule of signs~\cite{Jameson2006}, for each $j \in \mathcal{L}$, $t_s^\star$ has at most 1 real solution if $\sigma_l^2 \ne \sigma_{l'}^2$, $l,l' \in \mathcal{L}$.

				% if $\sigma_l^2 \ne \sigma_{l'}^2$, $l,l' \in \mathcal{L}$, then $t_s^\star$ has at most 1 real solution.

				% for a given $j$, $t_s^\star$ has at most 1 real solution if $\sigma_l^2 \ne \sigma_{l'}^2$, $l,l' \in \mathcal{L}$.

				% Therefore,

				% it can be concluded that for a given $j$, the sequence $(a_{l,j})_{l=1}^{L}$ only change sign once. Plugging~\eqref{eq:energy_distribution} into~\eqref{eq:kkt_thresholding_explicit}, we have
				% \begin{equation}
				% 	\sum_l a_{l,j} e^{-{t_s^\star}/{\sigma_l^2}} = 0,
				% 	\label{eq:optimal_thresholding_condition}
				% \end{equation}
				% where the LHS is a generalized Dirichlet polynomial. By Descartes' rule of signs~\cite{Jameson2006}, for a given $j$, $t_s^\star$ has at most 1 real solution if $\sigma_l^2 \ne \sigma_{l'}^2$, $l,l' \in \mathcal{L}$.

				% he number of positive roots is at most the number of sign changes in the sequence of polynomial's coefficients
				% and by Descartes' rule of signs has at most $L-1$ distinct real roots if $\sigma_i^2 \ne \sigma_j^2$, $i,j \in \mathcal{L}$.

				% % As proved by~\cite{Nguyen2020a}, the optimal backward channel quantizer
				% % \begin{equation}
				% % 	\sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(t_s^\star \mid x_l) = 0,
				% % \end{equation}
				% where $j \equiv s \pmod L$. Since the
				% % We notice that for a given $j$, $a_l \triangleq P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)}$ is a constant for all $s \equiv j \pmod L$. Plugging~\eqref{eq:energy_distribution} into \eqref{eq:kkt_thresholding_explicit}, we have
				% \begin{equation}
				% 	\sum_l a_{l,j} e^{-{h_s}/{\sigma_l^2}} = 0,
				% 	\label{eq:optimal_thresholding_condition}
				% \end{equation}
				% where the LHS is a Dirichlet polynomial and by Descartes' rule of signs has at most $L-1$ distinct real roots if $\sigma_i^2 \ne \sigma_j^2$, $i,j \in \mathcal{L}$.
				% % where the directional derivative can be explicitly written as
				% % \begin{subequations}
				% % 	\begin{align}
				% % 		\nabla_{t_{s'}^\star} I^\star_{\mathrm{B}}(c_{\mathcal{K}};z)
				% % 		& = \sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(h_s \mid x_l)\\
				% % 		& = 1
				% % 	\end{align}
				% % \end{subequations}
			\end{proof}

@@

				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^\star$ to maximize the weighted sum primary-backscatter rate are that, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,

@@

						I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) & = I^\star(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^\star(\bar{c}_{m_k}) > 0,\label{eq:probable_states}\\
						I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) & \le I^\star(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^\star(\bar{c}_{m_k}) = 0.\label{eq:dropped_states}

@@

						- \nabla_{P_k^\star(\bar{c}_{m_k})} I^\star(c_{\mathcal{K}};\boldsymbol{y},z) + \nu_k^\star - \lambda_{k,m_k}^\star = 0,

@@

						\lambda_{k,m_k}^\star = 0, \quad P_k^\star(\bar{c}_{m_k}) > 0,

@@

						\lambda_{k,m_k}^\star \ge 0, \quad P_k^\star(\bar{c}_{m_k}) = 0,

@@

					\nabla_{P_k^\star(\bar{c}_{m_k})} I^\star(c_{\mathcal{K}};\boldsymbol{y},z) = I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).

@@

				Due to the necessity and sufficiency of the \gls{kkt} conditions, we conclude that any input probability distribution $\boldsymbol{P}^\star$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
				\begin{subequations}
					\begin{alignat}{2}
						I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) & = \nu_k^\star + (1 - \rho), \quad && P_k^\star(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
						I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) & \le \nu_k^\star + (1 - \rho), \quad && P_k^\star(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
					\end{alignat}
				\end{subequations}
				which implies
				\begin{equation}
					\sum_{m_k} P_k^\star(\bar{c}_{m_k}) I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) = \nu_k^\star + (1 - \rho).
				\end{equation}

				On the other hand, by definition of marginations \eqref{eq:backscatter_sum_rate_expectation}, \eqref{eq:primary_ergodic_rate_expectation} and weighted summations \eqref{eq:weighted_sum_marginal_information}, \eqref{eq:weighted_sum_rate}, we have
				\begin{equation}
					\sum_{m_k} P_k^\star(\bar{c}_{m_k}) I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) = I^\star(c_{\mathcal{K}};\boldsymbol{y},z),
				\end{equation}
				which is irrelevant to $k$. It suggests $I^\star(c_{\mathcal{K}};\boldsymbol{y},z) = \nu_k^\star + (1 - \rho)$, $\forall k \in \mathcal{K}$, and completes the proof.
			\end{proof}

@@

				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_k(\bar{c}_{m_k})$ and is maximized at $\nabla_{P_k^\star(\bar{c}_{m_k})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, namely

@@

					S_k'(\bar{c}_{m_k}) - S_k'(\bar{c}_{i_k}) + (1 - \rho) \log \frac{P_k(\bar{c}_{i_k})}{P_k^\star(\bar{c}_{m_k})} = 0,

@@

				% 		P_k^\star(\bar{c}_{m_k})

@@

						P_k^\star(\bar{c}_{m_k})

@@

				where we define $u_k'(\bar{c}_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k'(\bar{c}_{m_k};\boldsymbol{y},z) \right)$. Although $P_k(\bar{c}_{i_k}) = 1 - \sum_{m_k \ne i_k} P_k^\star(\bar{c}_{m_k})$ is not guaranteed to be optimal, it has exactly the same form as \eqref{eq:optimal_relative_distribution}. In such case, the solution of choosing $i_k$ as reference would coincide with that of choosing any $m_k \ne i_k$ as reference, while optimality for $i_k$ is guaranteed in the latter case. Therefore, for a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $\forall i_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$, \eqref{eq:optimal_relative_distribution} ensures

@@

				We then prove any converging point of sequence \eqref{eq:optimal_distribution}, denoted as $P_k^\star(\bar{c}_{m_k})$, fulfills the optimal conditions \eqref{eq:optimal_conditions} and achieves the weighted primary-backscatter sum capacity. To see this, define
				\begin{equation}
					D_k^{(r)}(\bar{c}_{m_k}) \triangleq \frac{P_k^{(r+1)}(\bar{c}_{m_k})}{P_k^{(r)}(\bar{c}_{m_k})} = \frac{u_k^{(r)}(\bar{c}_{m_k})}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k^{(r)}(\bar{c}_{m_k'})},
				\end{equation}
				where $P_k^{(0)}(\bar{c}_{m_k}) > 0$. As sequence \eqref{eq:optimal_distribution} is convergent, any state with $P_k^\star(\bar{c}_{m_k}) > 0$ need to satisfy $D_k^\star(\bar{c}_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(\bar{c}_{m_k}) = 1$, namely
				\begin{equation}
					I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^\star(\bar{c}_{m_k'}) u_k^\star(\bar{c}_{m_k'}),
				\end{equation}
				which coincides with \eqref{eq:probable_states_marginal} and implies \eqref{eq:probable_states}. That is, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^\star(\bar{c}_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
				On the other hand, we assume $P_k^\star(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^\star(\bar{c}_{m_k}) = 0$,
				% On the other hand, we show if $P_k^\star(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:optimal_distribution}. By this assumption, for any state with $P_k^\star(\bar{c}_{m_k}) = 0$,
				\begin{equation}
					I_k^\star(\bar{c}_{m_k};\boldsymbol{y},z) > I^\star(c_{\mathcal{K}};\boldsymbol{y},z) = \sum_{m_k'} P_k^\star(\bar{c}_{m_k'}) I_k^\star(\bar{c}_{m_k'};\boldsymbol{y},z),
				\end{equation}
				where the equality origins from \eqref{eq:backscatter_sum_rate_expectation} and \eqref{eq:primary_ergodic_rate_expectation}. Since the exponential function is monotonically increasing, we have $u_k^\star(\bar{c}_{m_k}) > \sum_{m_k'} P_k^\star(\bar{c}_{m_k'}) u_k^\star(\bar{c}_{m_k'})$ and $D_k^\star(\bar{c}_{m_k}) > 1$. Considering $P_k^{(0)}(\bar{c}_{m_k}) > 0$ and $P_k^\star(\bar{c}_{m_k}) = 0$, it contradicts with
				\begin{equation}
					P_k^{(r)}(\bar{c}_{m_k}) = P_k^{(0)}(\bar{c}_{m_k}) \prod_{n=1}^r D_k^{(n)}(\bar{c}_{m_k}).
				\end{equation}
				Therefore, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^\star(\bar{c}_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.
